---
title: Under 25 vs Over 25 - Olympic Athletes

# to produce blinded version set to 1
blinded: 0

authors: 
- name: Steven Leung
  affiliation: MDS
- name: Brandon Lam
  affiliation: MDS
- name: Sam Quist
  affiliation: MDS
- name: Ruben De la Garza
  affiliation: MDS
 
keywords:
- data science curriculum, exploratory data analysis, data visualization, modeling, reproducibility, R, hypothesis test

bibliography: ../bibliography.bib
output:
  html_document:
    toc: true
    toc_depth: '4'
  
knit: (function(inputFile, encoding) {
  rmarkdown::render(inputFile, encoding = encoding, output_dir = "../doc") })
---

```{r blinding, echo=FALSE}
blind <- FALSE
```


```{r load-packages, include=FALSE}
library(tidyverse)
library(infer)
library(broom)
library(knitr)
library(scales)
library(kableExtra)
```

```{r code-font-size, echo=FALSE}
def.chunk.hook <- knitr::knit_hooks$get("chunk")
knitr::knit_hooks$set(chunk = function(x, options) {
 x <- def.chunk.hook(x, options)
 ifelse(options$size != "normalsize", paste0("\\", options$size,"\n", x, "\n \\normalsize"), x)
})
options(scipen = 0, digits = 3)
```

# Summary

# Introduction

It is known that olympic athletes require to train year after year for their shot at winning a medal for their country. In addition to physical strenght, the right mental state is very important for success in these events. It is a common conception to think that the younger the athlete, the stronger. But is that enough to win a medal? Does experience play a more important role? For this project we will attempt to make a hypothesis test to answer the question - is the proportion of athletes younger than 25 that win a medal greater than the proportion of athletes of age 25 or older that win a medal?

**Limitations and assumptions**:

# Methods

R programming language [@R] and the following R packages were used to perform the analysis:

- tidyverse [@tidyverse]

- knitr [@knitr]

- infer [@infer]

- broom [@broom]

- docopt [@docopt]

Also, python language [@python] and the following packages were used for the EDA:

- os [@os]

- altair [@vanderplas2018altair]

- pandas [@pandas]

```{r eda, child="../results/03_EDA_final_report.Rmd"}

```

# Results & Discussion


# References
