---
title: Under 25 vs Over 25 - Olympic Athletes

# to produce blinded version set to 1
blinded: 0

author: "Steven Leung, Brandon Lam, Sam Quist, Ruben De la Garza"
date: "2021/11/26 (updated: `r Sys.Date()`)"
 
keywords:
- data science curriculum, exploratory data analysis, data visualization, modeling, reproducibility, R, hypothesis test

bibliography: ../bibliography.bib

always_allow_html: true
output:
  html_document:
    toc: true
    toc_depth: '4'
  md_document:
    toc: true
    toc_depth: '4'
---

```{r blinding, echo=FALSE}
blind <- FALSE
```


```{r load-packages, include=FALSE}
library(tidyverse)
library(infer)
library(broom)
library(knitr)
library(scales)
library(kableExtra)
```

```{r code-font-size, echo=FALSE}
def.chunk.hook <- knitr::knit_hooks$get("chunk")
knitr::knit_hooks$set(chunk = function(x, options) {
 x <- def.chunk.hook(x, options)
 ifelse(options$size != "normalsize", paste0("\\", options$size,"\n", x, "\n \\normalsize"), x)
})
options(scipen = 0, digits = 3)
```

# Summary

Here we attempt to perform a hypothesis test on the question is the proportion of athletes younger than 25 that win a medal greater than the proportion of athletes of age 25 or older that win a medal?. Our final result was very conclusive, since we got a p-value of 1 in our hypothesis test. We used simulation methods to generate our null hypothesis and placed our observed test statistic on it to find a visually consistent answer with the p-value. We did not have enough statistical evidence to say that the proportions mentioned are not equal.

# Introduction

It is known that olympic athletes require to train year after year for their shot at winning a medal for their country. In addition to physical strenght, the right mental state is very important for success in these events. It is a common conception to think that the younger the athlete, the stronger and the more likely it is for him/her to win a spot on the podium. But is that enough to win a medal? Does experience play a more important role? For this project we will attempt to make a hypothesis test to answer the question - is the proportion of athletes younger than 25 that win a medal greater than the proportion of athletes of age 25 or older that win a medal?

**Limitations and assumptions**: 

- The age threshold of 25 years old was chosen on intuition. If time was provided, a way to make this analysis more robust would be to make some research and talk to some domain experts to find out if 25 years old is a good threshold to set for this hypothesis test.

- The data set contains information from the years 1896 - 2016, therefore, the analysis is taking into consideration all of these records, and the result should be interpreted as the comparison of the proportions mentioned within that time span. The analysis could be improved and give more specific insight if athletes were grouped by years (for example, before 1950 and after 1950) or by season (winter/summer games).

# Methods

R programming language [@R] and the following R packages were used to perform the analysis:

- tidyverse [@tidyverse]

- knitr [@knitr]

- infer [@infer]

- broom [@broom]

- docopt [@docopt]

- kableExtra [@kableExtra]

Also, python language [@python] and the following packages were used for the EDA:

- os [@os]

- altair [@vanderplas2018altair]

- pandas [@pandas]

```{r eda, child="../results/03_EDA_final_report.Rmd"}
```

# Hypothesis Test

```{r eda, child="../results/04_htest_final_report.Rmd"}
```

The results show that athletes under 25 have not been more successful in the olympics in comparison to athletes who are 25 and older. We can attribute this result to two different factors:

1. The olympics have many different types of events, and these events have been changing through the years. Many of these sports are dominated by older athletes, since they require more experience and hours put into the sport, rather than physical dexterity. Examples for these events could be art competitions (sculpturing, music, among others in the 1940's), archery (1900's), shooting (1900's).

2. For the majority of events, experience still plays a very important role in winning a medal.


# References
